Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-13 talk/iwtc11/paper.tex
Explain numpy benchmark, start writing down limitations paragraph. I'm not even sure how much limitations paragraph belongs there.

@@

\subsection{Numpy}
XXX: Fijal?

\subsection{Prolog}
XXX: Carl?

>>>>

\section{Limitations}

XXX as of now?

Loop invariant code motion as described has certain amount of limitations
that prevent it from speeding up larger loops. Those limitations are a target
of future work and might be lifted. Most important ones:

\begin{itemize}
\item Bridges are not well supported - if the flow is more complex than a single
      loop, the bridge might need to jump to the beginning of the preamble,
      making the optimization ineffective
\item XXX write about flushing caches at calls?
\end{itemize}

@@

\subsection{Numpy}

As a part of the PyPy project, we implemented small numerical kernel for
performing matrix operations. The exact extend of this kernel is besides
the scope of this paper, however the basic idea is to unroll a series of
array operations into a loop compiled into assembler. LICM is a very good
optimization for those kind of operations. The example benchmark performs
addition of five arrays, compiling it in a way that's equivalent to C's:

\begin{figure}
\begin{lstlisting}[mathescape,basicstyle=\setstretch{1.05}\ttfamily\scriptsize]
for (int i = 0; i < SIZE; i++) {
   res[i] = a[i] + b[i] + c[i] + d[i] + e[i];
}
\end{lstlisting}
\end{figure}

Where $res$, $a$, $b$, $c$, $d$ and $e$ are $double$ arrays.

\Subsection{Prolog}
XXX: Carl?
